# Results


```{r data, echo = TRUE, eval = FALSE}


p_data = read.csv(here("data", "tidy", "tidy_data.csv")) %>% 
  filter(!is.na(participant))


#### Accuracy


totals_n = p_data %>% # create df for overall accuracy
  group_by(type, is_correct) %>% 
  summarise(n = n()) %>% 
  pivot_wider(names_from = is_correct, values_from = n) %>% 
  rename("correct" = "1") %>% 
  rename("incorrect" = "0") %>% 
  mutate(total = correct + incorrect) %>% 
  mutate(pct_correct = correct/total) %>% 
  select(type, pct_correct)

ind_data = p_data %>% # create df for indivudual accuracy
  group_by(participant, type, is_correct) %>% 
  summarize(n = n()) %>% 
  pivot_wider(names_from = is_correct, values_from = n) %>% 
  rename("correct" = "1") %>% 
  rename("incorrect" = "0")


ind_data[is.na(ind_data)] <- 0

neat_ind_data = ind_data %>% 
  mutate(total = correct + incorrect) %>% 
  mutate(pct_correct = correct/total) %>% 
  select(participant, type, pct_correct) %>% 
  pivot_wider(names_from = type, values_from = pct_correct)
  
```

```{r accuracy, echo = TRUE, eval = FALSE}
totals_n %>% 
  filter(type != "pseudoword") %>%
  mutate(pct_correct = 100*pct_correct) %>% 
  mutate(type = factor(
    type,
    levels = c("non_cognate", "two_way_cognate", "three_way_cognate"),
    labels = c("Non-cognate", "Two-way cognate", "Three-way cognate")
  )) %>% 
  ggplot(aes(x = type, y = pct_correct)) + theme_minimal() + geom_col(color = "black", fill = "seagreen4") + ylim(0,100) + custom_theme() + xlab("") +
  ylab("Overall percentage of correct Trials")

```


Figure \@ref(fig:accuracy) shows the overall accuracy within the entire data set (`r nrow(p_data)` trials) excluding pseudowords (in which `r round2(totals_n$pct_correct[2])`% of trials were correct).
Overall, three-way cognates were the most accurate (`r round2(totals_n$pct_correct[3])`%), followed by two-way cognates (`r round2(totals_n$pct_correct[4])`%), while non-cognates were the least accurate (`r round2(totals_n$pct_correct[1])`%).

Indivual accuracy ranged from...

```{r}
neat_ind_data %>% 
  pivot_longer(cols = `non_cognate`:`two_way_cognate`, names_to = "type", values_to = "accuracy") %>% 
  ggplot(aes(x = accuracy)) + theme_minimal() + geom_histogram(binwidth = .2, color = "black", fill = "skyblue2") + facet_wrap(~type) + custom_theme()


```


```{r}

rts = p_data %>% 
  group_by(participant, type) %>% 
  summarise(mean_rt = mean(key_resp_lextale_trial.rt), sd_rt = sd(key_resp_lextale_trial.rt), n = n())

neat_ind_data %>% 
  pivot_longer(cols = `non_cognate`:`two_way_cognate`, names_to = "type", values_to = "accuracy") %>%
  left_join(rts, by = c("participant", "type")) %>% 
  ggplot(aes(x = accuracy, y = mean_rt)) + geom_point() + theme_minimal() + geom_smooth(method = "lm") + custom_theme() + facet_wrap(~type)
  
```
